Supporting Information

### 2022-03-30 Manuscript/Supplementary_Material/Supporting_information_Functional_Ecology.Rmd
Update Supporting_information_Functional_Ecology.Rmd

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity",scale="response", by="Group",line.par = list(col = 'black'),points=list(size=0),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Specialization") + ylab("Percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
    ggtitle("Floral visitors")+ylim(-0.15,1)+geom_point(data=pollinator_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.5)

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",scale="response",points=list(size=0),
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Specialization") + ylab("Percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
  ggtitle("Plants")+ylim(-0.15,1)+geom_point(data=plant_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.5)

>>>>

pollinators_sp_plot <- visreg(model_freq_specif_ind, "Specificity",scale="response", by="Group",line.par = list(col = 'black'),points=list(size=0),
                         strip.names=c("Bee",
                                       "Coleoptera",
                                       "Lepidoptera",
                                       "Non-bee-Hymenoptera",
                                       "Non-syrphids-diptera",
                                       "Syrphids"),gg = TRUE) + theme_bw() +
  xlab("Specialization") + ylab("Percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+ scale_fill_grey(start=0.5, end=0.8) +
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
    ggtitle("Floral visitors")+ylim(-0.15,1)+geom_point(data=pollinator_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.1)

plants_sp_plot <- visreg(model_freq_specif_ind_plant, "Specificity",line.par = list(col = 'black'), by="Group",scale="response",points=list(size=0),
       strip.names=c("Selfing herbs",
                     "Small outcrossing perennials",
                     "Self-incompatible perennials\nwith large flowers",
                     "Tall plants with small\nunisexual flowers",
                     "Short-lived outcrossers with\nlong zygomorphic flowers"),gg = TRUE)+ theme_bw() +
  xlab("Specialization") + ylab("Percentile")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.5))+
   theme(strip.text.x = element_text(size = 12),plot.title = element_text(hjust = 0.5, size = 23))+
  ggtitle("Plants")+ylim(-0.15,1)+geom_point(data=plant_freq_position_s_ind, aes(Specificity,Percentil), alpha=0.1)
